
% -------------- Resume ---------------
\documentclass{resume}

\begin{document}
% --------- Contact Information -----------
\introduction[
    fullname={Nihal Raj},
    email={nihalraj8235@gmail.com},
    phone={+91-8340144754},
    linkedin={linkedin.com/in/nihal-raj-2193ab235/},
    github={github.com/rajnihal},
    portfolio={nihal-raj.netlify.app/}
]
% --------- Summary -----------
\summary{I am pursuing a B.Tech degree specializing in Information Technology at Vellore Institute of Technology, with skills in software engineering, web development, and mobile app development 
\vspace{0.8 em}using C/C++, Kotlin, JavaScript, and Python.}
% --------- Education ---------
\begin{educationSection}{Education}
    \educationItem[
        university={Vellore Institute of Technology},
        college={Vellore, Tamil Nadu},
        graduation={June 2024},
        grade={},
        program={B.Tech,Information Technology},
        coursework={Big Data, Cloud Computing, AI, ML, IoT, Software Testing, Web Development.},
    ]
\end{educationSection}

% --------- Skills -----------
\begin{skillsSection}{Technical Skills}
    \skillItem[
        category={Programming},
        skills={C++, Kotlin,Flutter, JavaScript, HTML, CSS, Python (pandas, NumPy, scikit-learn, matplotlib).}
    ] \\
    \skillItem[
        category={Developer Tools},
        skills={Android Studio, VS Code, Git, GitHub, npm (node), Netlify, API.}
    ] \\
    \skillItem[
        category={Frameworks},
        skills={Node.Js, Express.Js,React.Js,Bootstrap }
    ] \\
    \skillItem[
        category={Cloud/Databases},
        skills={MongoDB, SQL and NOSQL.}
    ]\\
    \skillItem[
        category={Prompt Engineering},
        skills={Skilled in optimizing NLP models and enhancing AI performance through advanced engineering techniques, with a focus on improving output quality in diverse AI and ML applications.}
    ]
\end{skillsSection}
% --------- Experience -----------
\begin{experienceSection}{Professional Experience}
    \experienceItem[
        company={Bahwan Cybertek},
        location={Bengaluru, Karnataka},
        position={Flutter Intern},
        duration={Jan 2024 – Present}
    ]
    \begin{itemize}
        \itemsep -6pt {}
        \item Developed and maintained mobile applications using Flutter framework, ensuring high performance and reliability across multiple platforms.
    \end{itemize}

    \experienceItem[
        company={SmartInternz (Google-Developers)},
        location={Remote},
        position={Android Development Intern},
        duration={May 2023 – July 2023}
    ]
    \begin{itemize}
        \itemsep -6pt {}
        \item Designed and developed 5 Android apps with Jetpack Compose, enhancing engagement, accessibility, and user satisfaction.
        \item Improved speech recognition accuracy by 30 percent with Jetpack Compose, implementing custom voice recognition features.
    \end{itemize}

\end{experienceSection}
% --------- Projects -----------
\begin{experienceSection}{Academic projects}

    
        \projectItem[
        title={RecordPad || \href{https://github.com/rajnihal/RecordPad_Android}{Link}},
        duration={May 2023 – July 2023},
        keyHighlight=\textit{Android App transforming spoken words into text effortlessly.}
    ]
    \begin{itemize}
        \vspace{-0.4em}
        \itemsep -6pt {}
        \item Implemented an inclusive speech-to-text solution, increasing accuracy by 10 percent and enabling notetaking, language learning, and 
voice control.
        
       
    \end{itemize}
    \projectItem[
        title=Image Generation using Stable Diffusion and IEA Algorithm || \href{https://colab.research.google.com/github/rajnihal/Image_Generation_using_stableDiffusion_and_IEA_Algorithm/blob/main/Image_Generation_using_Stable_diffusion_and_IEA_Algorithm.ipynb}{Link},
        duration=Jan 2024 - May 2024,
        keyHighlight= \textit{Positioned project as a significant advancement in AI-driven image generation.}
    ]
    \begin{itemize}
        \vspace{-0.4em}
        \itemsep -6pt {}
        \item Implemented an AI-driven Image Generation project integrating Stable Diffusion Model, text-to-image generation, IEA-based user feedback, and post-processing within a unified architecture.
    \end{itemize}

\end{experienceSection}
% --------- Activities -----------
\begin{experienceSection}{Positions of Responsibility}
    \projectItem[
        title={Senior committee Member || VIT-Stellar },
        keyHighlight={\textit{ Part of 30-member team to conduct the event and researched about space technology.}},
        duration={Jan 2022 – Jan 2023}
    ]\end{experienceSection}
    \projectItem[
    title={Club Member || Smile over Stress, Fitness and beyond},
    keyHighlight={\textit{  Part of committee member, achieved wellness event success, fostering positivity and engagement.}},
    duration={Jan 2023 – Jan 2024}
    ]


% --------- Other work experience -----------
\begin{experienceSection}{Other work experience}
    \experienceItem[
        company={JP Morgan Chase Software Engineering Virtual Experience},
        location={Remote},
        position={SDE},
        duration={May 2023 - October 2023}
    ]
    \begin{itemize}
        \vspace{-0.2em}
        \itemsep -6pt {}
        \item Employed Python, Git and React.js for 3 projects, boosting team efficiency by 20 percent.
        \item Integrated Perspective open-source code and JPMC Cooperation’s tools for projects that raised user engagement by 30 percent.
    \end{itemize}

\end{experienceSection}


\end{document}
